Setting up Data

### 2019-11-12 src/SetupData.Rmd
added batch17 female counts

AP_mouse_table <- add_strain(AP_mouse_table.HQ)
AP_mouse_table.HQ <- add_subsp(AP_mouse_table.HQ)
AP_mouse_table.HQ <- add_sex(AP_mouse_table.HQ)
AP_mouse_table.HQ <- add_category(AP_mouse_table.HQ)

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_11.11.19.RData")

>>>>

AP_mouse_table.HQ <- add_strain(AP_mouse_table.HQ)
AP_mouse_table.HQ <- add_subsp(AP_mouse_table.HQ)
AP_mouse_table.HQ <- add_sex(AP_mouse_table.HQ)
AP_mouse_table.HQ <- add_category(AP_mouse_table.HQ)

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_11.12.19.RData")
